Constructing the transition graphs of interacting hysterons

### 2022-06-03 Paper_draft.tex
Added comment that term GoE states is customary
Added scrambled graphs to base graphs fig that are possible for general, but not linear coupling

It often occurs that one or more of the possible states for $N$ hysterons cannot be reached from the ground state. We refer to such states which cannot be reached as garden-of-Eden states. Because the transitions from garden-of-Eden states are irrelevant when one starts from the ground state, as is generally the case in our experiments, we may choose to ignore garden-of-Eden states. As a consequence, when two graphs only differ from one another by transitions that occur from garden-of-Eden states, the graphs become duplicates. Therefore, when garden-of-Eden states are ignored, the number of distinct graphs can turn out lower than the number of possible combinations of transitions. For $N=2$, ignoring garden-of-Eden states  reduces the number of graphs from 1458 to 752. 

@@

    \caption{All possible base graphs for the two- and three-hysteron systems. a) All base graphs for $N=2$; since scrambling is not possible for $N=2$, the base graphs are the two Preisach graphs. b) Preisach graphs for $N=3$. c) Scrambled base graphs for N=3 that are possible for linear coupling.}

>>>>

It often occurs that one or more of the possible states for $N$ hysterons cannot be reached from the ground state. As is customary, we refer to states that cannot be reached as garden-of-Eden states. Because the transitions from garden-of-Eden states are irrelevant when one starts from the ground state, as is generally the case in our experiments, we may choose to ignore garden-of-Eden states. As a consequence, when two graphs only differ from one another by transitions that occur from garden-of-Eden states, the graphs become duplicates. Therefore, when garden-of-Eden states are ignored, the number of distinct graphs can turn out lower than the number of possible combinations of transitions. For $N=2$, ignoring garden-of-Eden states  reduces the number of graphs from 1458 to 752. 

@@

    \caption{All possible base graphs for the two- and three-hysteron systems. a) All base graphs for $N=2$; since scrambling is not possible for $N=2$, the base graphs are the two Preisach graphs. b) Preisach graphs for $N=3$. c) Scrambled base graphs for N=3 that are possible for linear coupling. d) Scrambled base graphs that are possible for general, but not linear model.}
